---
title: "Movie Rating"
author: Peiyun Zhou
output: pdf_document
---

This R Markdown document demonstrates how to preprocess the movies dataset and 
explore different questions about relationships between Audience/Critics ratings and Budget, Genre, and Year. 

First, we load the dataset "movie_rating.csv", rename the variables, 
and set Year as a factor variable. 

```{r echo=TRUE}
movies<-read.csv("Movie-Ratings.csv")
head(movies) # Explore the dataset
colnames(movies)<-c("Film","Genre","CriticRating","AudienceRating","BudgetMillions","Year") # rename the columns
head(movies) # Recheck the dataset
# tail(movies)
str(movies) # check the structure of the variables in the dataset
movies$Year<-as.factor(movies$Year) # Set year as a factor variable
```


Load the library for visualization
Use aec() to map the data to what you want to see
Right now we will not see any informaiton about the data

```{r, echo=TRUE}
library(ggplot2)
ggplot(data=movies,aes(x=CriticRating,y=AudienceRating))

```


We need to add the geometry layer

```{r, echo=TRUE}
ggplot(data=movies,aes(x=CriticRating,y=AudienceRating))+
    geom_point()
```

We can assign more parameters to the geometry, such as color, size

```{r, echo=TRUE}

# Color based on Genre
ggplot(data=movies,aes(x=CriticRating,y=AudienceRating,
                       color=Genre)) +
  geom_point()
# Size and Color based on Genre
ggplot(data=movies,aes(x=CriticRating,y=AudienceRating,
                       color=Genre,size=Genre)) +
  geom_point()

# Color based on Genre; Size based on Budget
ggplot(data=movies,aes(x=CriticRating,y=AudienceRating,
                       color=Genre,size=BudgetMillions)) +
  geom_point()
```

We can add  Geom layer, such as points and lines, or multiple layers
Yet, when we add points and lines, the plot is not very informative
We should override Aesletics to make the plot more informative

```{r, echo=TRUE}


p<-ggplot(data=movies,aes(x=CriticRating,y=AudienceRating,
                       color=Genre,size=BudgetMillions)) +
  geom_point()

# Add Geom layer--Points
p+geom_point()

# Add Geom layer--Lines
p+geom_line()

#Add multiple Geom layers
p+geom_line()+geom_point()
```

```{r, echo=TRUE}
# Overriding Aesletics Example 1, override Size
p+geom_point(aes(size=CriticRating))

# Overriding Aesletics Example 2, override Color
# p+geom_point(aes(color=BudgetMillions))

# Overriding Aesletics Example 3, override X
p+geom_point(aes(x=BudgetMillions))+
  xlab("Budget Millions $$$")
# Overriding Aesletics Example 4, reduce line size
p+geom_line(size=1) + geom_point()

```

There are differences between mapping and setting
When you want to set a color, you do NOT use aes
When you want to map a color to a variable, you use aes

```{r,echo=TRUE}
#1. Mapping
p+geom_point(aes(size=BudgetMillions))
#2. Setting
p+geom_point(size=10)
```

We can also create histographs to visualize the Audience's or Cristic's rating based on different predictors (e.g. Genre)

```{r,echo=TRUE}

s<-ggplot(data=movies,aes(x=BudgetMillions))
s+geom_histogram(binwidth=10)
# Add color for each genre
s+geom_histogram(binwidth=10,aes(fill=Genre))
# Add a black boarder line
s+geom_histogram(binwidth=10,aes(fill=Genre),color="Black")
```

We can also create density charts to explore the data
We found that Audiences' ratings showed a normal distribution while
the Critics' ratings exhibited an uniform distribution 


```{r,echo=TRUE}

s<-ggplot(data=movies,aes(x=BudgetMillions))
s+geom_density(aes(fill=Genre))
s+geom_density(aes(fill=Genre),position="stack")

# Starting Layers Tips 
t<- ggplot(data=movies,aes(x=AudienceRating))
t+geom_histogram(binwidth = 10,fill="White",color="Blue")

# Another way to make the same plot
t<- ggplot(data=movies)
# Distribution of the Audience Rating; The trend is normal distribution 
t+geom_histogram(binwidth = 10,
                 aes(x=AudienceRating),
                     fill="White",color="Blue")

# Distribution of the Critics Rating; The trend is an uniform distribution
t+geom_histogram(binwidth = 10,
                 aes(x=CriticRating),
                 fill="White",color="Blue")
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
