---
title: "Movie Rating Part2 Rcodes"
author: Peiyun Zhou
output: pdf_document
---

I will further demonstrates how to create boxplot, adjust the scale of the plots, and 
label the plots in this R Markdown document. These data visualization will help us to inspect the relationships between Audiences'/Critics' move ratings and budget, genre, year, ect. 

First, load the dataset and rename the columns
```{r echo=TRUE}
movies<-read.csv("Movie-Ratings.csv")
colnames(movies)<-c("Film","Genre","CriticRating","AudienceRating","BudgetMillions","Year") # rename the columns
movies$Year<-as.factor(movies$Year) # Set year as a factor variable
```

Load the library for visualization

```{r, echo=TRUE}
library(ggplot2)
```


We can see how the audience rating changes based on the change of the critics rating
using the smooth function in the ggplot

```{r, echo=TRUE}
u<-ggplot(data=movies,aes(x=CriticRating,y=AudienceRating,color=Genre))
u+geom_point()+geom_smooth(fill=NA)

```

We can further explore how Audiences' ratings differ based on different genre 
through building boxplots

```{r, echo=TRUE}
u<-ggplot(data=movies,aes(x=Genre,y=AudienceRating,color=Genre))
u+geom_boxplot()
u+geom_boxplot(size=1.2) # Change the size of the boxplot
u+geom_boxplot(size=1.2)+geom_jitter() # Include the dots
```

Another way to create boxplot for Audience Rating with manipulation of the transparency of the data points

```{r,echo=TRUE}
u+geom_jitter()+geom_boxplot(size=1.2,alpha=0.5)
```

We can also explore how Cristics' ratings change depend on the genre.


```{r,echo=TRUE}
b<-ggplot(data=movies,aes(x=Genre,y=CriticRating,color=Genre))
b+geom_boxplot(size=1.2)+geom_jitter()
# Another way to create boxplot for Critics Rating:
b+geom_jitter()+geom_boxplot(size=1.2,alpha=0.5)
```

We can use facet in the ggplot to seperate the histographs for movie budget based 
on the movie genres

```{r,echo=TRUE}
# Facets
v<-ggplot(data=movies,aes(x=BudgetMillions))
v+geom_histogram(binwidth=10,aes(fill=Genre),color="Black")

v+geom_histogram(binwidth=10,aes(fill=Genre),
                 color="Black")+
  facet_grid(Genre~.,scale="free")
```


Scatterplot can also be used to visualize the relationships between audiences' ratings and critics ratings based on genre

```{r,echo=TRUE}
w<-ggplot(data=movies,aes(x=CriticRating,y=AudienceRating,color=Genre))
w+geom_point(size=3)
w+geom_point(size=3)+
  facet_grid(Genre~.)
```

The relationships between audiences' ratings and critics ratings based on Year

```{r,echo=TRUE}
w+geom_point(size=3)+
  facet_grid(Year~.)
```


The relationships between audiences' ratings and critics ratings based on Year and Genre


```{r,echo=TRUE}
w+geom_point(size=3)+
  facet_grid(Genre~Year)
```


We can further adjust the scale of the plots

```{r,echo=TRUE}
m<-ggplot(data=movies,aes(x=CriticRating,y=AudienceRating,
                          size=BudgetMillions,
                          color=Genre))
m+geom_point()

m+geom_point()+
  xlim(50,100) # Zoom in and Remove rows that are outside the boundaries

m+geom_point()+
  xlim(50,100) +
  ylim(50,100) # Further Zoom in and remove columns that are outside the boundaries

```


The incorrect way to zoom in data will lead to trimmed data

```{r, echo=TRUE}
# This does not always work
n<-ggplot(data=movies,aes(x=BudgetMillions))
n+geom_histogram(binwidth = 10,aes(fill=Genre),color="Black")

n+geom_histogram(binwidth = 10,aes(fill=Genre),color="Black")+
  ylim(0,50) # This would trim the data, rather than zoom in 

```

The correct way to create zoom-in plot
Use coord_cartesian( )

```{r, echo=TRUE}
n+geom_histogram(binwidth = 10,aes(fill=Genre),color="Black")+
  coord_cartesian(ylim=c(0,50))  # Zoom in into the chart 
```



